Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-06 p2/axioms.tex
Added todo
Description of independent commands

It is intentional that we use the same symbol for independent commands
and sequences as for incomparable nodes. As the next
\namecref{incomparable_is_independent},
shows, these concepts are closely related.

\begin{mylem}\mlabel{incomparable_is_independent}
Two $\cxynv$ and $\czwmv$ are different commands,
and none of them is an assertion command, then
$\cxynv\indep\czwmv$ if and only if $n\unrel m$.
\end{mylem}
\begin{proof}
The right-to-left part is a restatement of
\cref{ax_separate_commute,ax_separate_nobreaks}.

We prove the left-to-right part by contradiction,
assuming that both $\cxynv\indep\czwmv$ and $n\nunrel m$.
From $n\nunrel m$
we know that $n=m$, $n\descendant m$ or $m\descendant n$.

If $n=m$, then from \cref{ax_same_breaks} we must have $[y]=[z]$ and $[w]=[x]$
as otherwise the commands, in one order or the other, would break all filesystems.
We also see that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $w=y$.
Therefore $n=m$, $[x]=[y]=[z]=[w]$ and $w=y$, which contradicts our assumption that the commands are different.

The remaining case is that $n\descendant m$ or $m\descendant n$.
If they are not directly related,
then from \cref{ax_distantrel_breaks} we know that
$\cxynv\cc\czwmv$ breaks all filesystems as they are not assertion commands,
which contradicts the assumption that the commands are independent.
From the construction and destruction pairs and 
\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
even if the nodes are directly related, either
$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
breaks all filesystems, so they again cannot be independent.
\end{proof}

>>>>

It is intentional that we use the same symbol for independent commands
and sequences as for incomparable nodes. As
\namecref{incomparable_is_independent},
shows, these concepts are closely related.

\begin{mycor}\mlabel{incomparable_is_independent}
If $\cxynv$ and $\czwmv$ are different commands,
and none of them is an assertion command, then
$\cxynv\indep\czwmv$ if and only if $n\unrel m$.
\end{mycor}

To prove this, we are going to prove the following lemma,
which characterizes independent commands in a more detailed way.

\begin{mylem}\mlabel{independent_details}
For two commands $\cxynv\indep\czwmv$ if and only if
one of the following holds:
\begin{itemize}
\item $n\unrel m$;
\item or $n=m$ and the commands are equivalent assertion or replacement commands;
\item or $n\descendant m$ or $m\descendant n$,
and either the command on the ancestor asserts a directory,
or the command on the descendant asserts an empty node (or both).
\end{itemize}
\end{mylem}

\begin{proof}
By definition we know that $\cxynv\cc\czwmv\equiv\wrksx{\czwmv\cc\cxynv}$.
The first case is a restatement of
\cref{ax_separate_commute,ax_separate_nobreaks}.
Otherwise $n\nunrel m$, in which case either $n=m$, or, without loss of generality, $n\descendant m$.

If $n=m$, then from \cref{ax_same_breaks} we must have $[y]=[z]$ and $[w]=[x]$
as otherwise the commands, in one order or the other, would break all filesystems.
The equivalence also implies $[x]=[z]$ as otherwise the two sides would not be defined on the same filesystem,
as well as $y=w$ as their effects is the same.
The two commands are therefore the same, and they are either assertion or replacement commands.

The remaining case is that $n\descendant m$.
If the nodes are not directly related, then \cref{ax_distantrel_breaks} gives
the conditions in the third case in the lemma.
If they are directly related, 
\cref{ax_directchild_breaks,ax_directparent_breaks}
gives the same conditions, while they also allow the commands being
a construction or destruction pair.
However, the reversals of construction and destruction pairs break all filesystems.
\end{proof}

\Cref{incomparable_is_independent} follows directly from \cref{independent_details}.
While equivalent commands can hardly be thought of as independent,
we retain this name for this relation as in most
cases we use it on pairs of different commands that are also not assertion commands.

### 2018-07-06 p2/rec-intro.tex
Description of independent commands

Whether two commands are independent is easy to determine programmatically
either based on \cref{def_indep} and the rules listed in \cref{section_axioms},
or based on \cref{incomparable_is_independent} 
in at most $O(x^2)$ time, where $x$ is the number of commands.
Then, to generate the sequence $\reca$ from the resulting set, 
we can order the commands using the algorithm described in
\cref{ordering} as $\reca$, being a subset of $A$, is also simple.

>>>>

Note that $\alpha$ is not an assertion command, and $\bmanp$ contains no assertion commands;
also, $\alpha\not\in\bmanp$, so independence in this case is equivalent to
the node $\alpha$ affects being incomparable to the nodes commands in $\bmanp$ affect.
Therefore whether two commands are independent is easy to determine programmatically
in at most $O(x^2)$ time, where $x$ is the number of commands. % TODO
Then, to generate the sequence $\reca$ from the resulting set, 
we can order the commands using the algorithm described in
\cref{ordering} as $\reca$, being a subset of $A$, is also simple.

### 2018-07-06 p2/rec-sound.tex
Description of independent commands

In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
We also know that because of {\condApr} there must be 
a command $\cqrov$ in $T$ which is not independent of $\czwmv$
as $\czwmv$ is not part of $S^*$.
% \begin{gather*}
% S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
% T = \cdots\cc  \cqrov\cc \cdots
% \end{gather*}
Based on \cref{incomparable_is_independent} we know this means that
either $m\descendantEq o$ or $o\descendantEq m$.
From {\condApr} we also know that $\cxynv\indep \cqrov$,
and so because of \cref{incomparable_is_independent},
$n\unrel o$.
We also know none of these commands is an assertion command, and 
from {\condDisj} that $\cqrov\neq\czwmv$.

>>>>

In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
We also know that because of {\condApr} there must be 
a command $\cqrov$ in $T$ which is not independent of $\czwmv$
as $\czwmv$ is not part of $S^*$.
% \begin{gather*}
% S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
% T = \cdots\cc  \cqrov\cc \cdots
% \end{gather*}
Based on \cref{incomparable_is_independent} we know this means that
either $m\descendantEq o$ or $o\descendantEq m$.
We know none of these commands is an assertion command, and 
from {\condDisj} that $\cqrov\neq\czwmv$.
Also, from {\condApr} we know that $\cxynv\indep \cqrov$,
and so because of \cref{incomparable_is_independent},
$n\unrel o$.

### 2018-07-06 p2/works-inverse.tex
Description of independent commands

\begin{mylem}\mlabel{combine_independent_commands}
The combination of independent commands is defined on all filesystems
where both of the commands are defined:
\[ \alpha\indep \beta \Rightarrow \worksmbx{\alpha, \beta}{\alpha\cc \beta}. \]
\end{mylem}
\begin{proof}
TODO: they are the same? FF? assertion commands?

In the following proof we reach back to our filesystem model.
Let $\alpha=\cxynv$ and $\beta=\czwmv$.
The proof is by contradiction;
assume that there is a filesystem $\FS$ for which
$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
$(\cxynv\cc \czwmv)\aFS=\fsbroken$.
We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
$\czwmv$ that breaks it.

@@

TODO continue here. Require not replacement?

>>>>

\begin{mylem}\mlabel{combine_independent_commands}
The combination of independent commands is defined on all filesystems
where both of the commands are defined:
\[ \alpha\indep \beta \Rightarrow \worksmbx{\alpha, \beta}{\alpha\cc \beta}. \]
\end{mylem}
\begin{proof}
% In the following proof we reach back to our filesystem model.
The proposition follows from \cref{independent_details},
and we follow the three cases listed there.

The first case is that $n\unrel m$ where $\alpha=\cxynv$, $\beta=\czwmv$.

TODO CONTINUE

Using an inverse proof we assume that for a filesystem $\FS$
both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\FS$ is broken.
We know a command breaks a filesystem either if
its input type is not compatible with the filesystem,
or if the filesystem ceases to have the tree property.

We also know that whether a filesystem has the tree property
depends

The second case is that the two commands are the same and are assertion or replacement
commands, when the proposition is trivially true.
Finally, the third case is that the two commands are on comparable nodes and one of them
is an assertion command, when the proposition is again trivially true.

TODO END

Let $\alpha=\cxynv$ and $\beta=\czwmv$.
The proof is by contradiction;
assume that there is a filesystem $\FS$ for which
$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
$(\cxynv\cc \czwmv)\aFS=\fsbroken$.
We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
$\czwmv$ that breaks it.

@@
